### 2024-03-04 README.Rmd

# Colors for all! <img src='inst/img/cols4all_logo.png' align="right" height="139" />

[![CRAN](http://www.r-pkg.org/badges/version/cols4all)](https://cran.r-project.org/package=cols4all) 
[![cran checks](https://cranchecks.info/badges/worst/cols4all)](https://cran.r-project.org/web/checks/check_results_cols4all.html)
[![Downloads](http://cranlogs.r-pkg.org/badges/cols4all?color=brightgreen)](http://www.r-pkg.org/pkg/cols4all)

>>>>

# Colors for all! <a href="https://mtennekes.github.io/cols4all/"><img src="man/figures/logo.png" align="right" height="138" alt="cols4all website" /></a>

<!-- badges: start --->
[![CRAN](https://www.r-pkg.org/badges/version/cols4all)](https://cran.r-project.org/package=cols4all) 
[![cran checks](https://cranchecks.info/badges/worst/cols4all)](https://cran.r-project.org/web/checks/check_results_cols4all.html)
[![Downloads](https://cranlogs.r-pkg.org/badges/cols4all?color=brightgreen)](https://www.r-pkg.org/pkg/cols4all)
<!-- badges: end --->
